DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-17 paper/main.tex
intro - overview revision
author style fix

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{fixme}
%\usepackage{authblk}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\author{\IEEEauthorblockN{Michael G. Bechtel}
\IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
\textit{University of Kansas}\\
Lawrence, USA \\
mbechtel@ku.edu}
\and
\IEEEauthorblockN{Elise McEllhiney}
\IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
\textit{University of Kansas}\\
Lawrence, USA \\
e908m428@ku.edu}
\and
\IEEEauthorblockN{Minje Kim}
\IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
\textit{Indiana University Bloomington}\\
Bloomington, USA \\
minje@indiana.edu}
\and
\IEEEauthorblockN{Heechul Yun}
\IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
\textit{University of Kansas}\\
Lawrence, USA \\
heechul.yun@ku.edu}
}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
% \usepackage{fixme}
%\usepackage{authblk}
\def\fixme#1{\typeout{FIXED in page \thepage : {#1}}
%  \bgroup \color{red}{} \egroup}
\bgroup \color{red}{[FIXME: {#1}]} \egroup}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\author{Michael G. Bechtel$^\dagger$, Elise McEllhiney$^\dagger$, Minje Kim$^\star$, Heechul Yun$^\dagger$\\
  $^\dagger$ University of Kansas, USA. \{mbechtel, e908m428, heechul.yun\}@ku.edu \\
  $^\star$ Indiana University, USA. minje@indiana.edu \\
}

%% \IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
%% \textit{University of Kansas}\\
%% Lawrence, USA \\
%% mbechtel@ku.edu}
%% \and
%% \IEEEauthorblockN{Elise McEllhiney}
%% \IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
%% \textit{University of Kansas}\\
%% Lawrence, USA \\
%% e908m428@ku.edu}
%% \and
%% \IEEEauthorblockN{Minje Kim}
%% \IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
%% \textit{Indiana University}\\
%% Bloomington, USA \\
%% minje@indiana.edu}
%% \and
%% \IEEEauthorblockN{Heechul Yun}
%% \IEEEauthorblockA{\textit{Electrical Engineering and Computer Science} \\
%% \textit{University of Kansas}\\
%% Lawrence, USA \\
%% heechul.yun@ku.edu}
%% }
